**Application of database-independent approach to assess the quality of OTU picking methods**

### 2016-03-26 papers/msystems_2016/Schloss_Commentary_mSystems_2016.Rmd
Keep TeX output file to conversion to docx

---
title: "**Application of database-independent approach to assess the quality of OTU picking methods**"
bibliography: references.bib
output:
  pdf_document:
    includes:
      in_header: header.tex
csl: msystems.csl
fontsize: 11pt
geometry: margin=1.0in
---

>>>>

---
title: "**Application of database-independent approach to assess the quality of OTU picking methods**"
bibliography: references.bib
output:
  pdf_document:
    keep_tex: true
    includes:
      in_header: header.tex
csl: msystems.csl
fontsize: 11pt
geometry: margin=1.0in
---
